Retrofitting Effect Handlers onto OCaml

### 2020-11-04 retro-concurrency.tex

>>>>

In this section, we evaluate the performance of Multicore OCaml effect handlers
against the performance requirements set in \S\ref{sec:req}. Multicore OCaml is
an extension of 4.10.0 OCaml compiler with support for shared memory
parallelism and effect handlers. These results were obtained on 2-socket,
Intel\textregistered Xeon\textregistered Gold 5120 x86-64 server, with 28
physical cores (14 cores on each socket), and 2 hardware threads per core. Each
core runs at 2.20GHz and has 32 KB of L1 data cache, 32 KB of L1 instruction
cache and 1MB of L2 cache. The cores on a socket share a 19.25 MB L3 cache. The
server has 64GB of main memory and runs Ubuntu 18.04.

\subsection{No effects benchmaks}

In this section, we measure the impact of the addition of effect handlers on
code that does not use effect handlers.

\newpage

\section*{Supplementary Material}

\section*{Evaluation Planning}
